Pruning Subsequence Search with Attention-Based Embedding

### 2015-09-24 paper.tex
Restructure sections, add conclusion.

In the following section, we discuss embedding and attention-based neural network models, which we use to motivate our proposed model in Section \ref{sec:model}.
In Section \ref{sec:experiment}, we evaluate the effectiveness of our proposed model on the task of matching musical transcriptions to audio recordings of their corresponding songs in a large database.
Finally, we discuss possibilities for improvement in Section \ref{sec:discussion}.

@@

\section{Pruning Experiment}

@@

@@

\section{Future Work}
\label{sec:discussion}

Larger embedding space.

More convolutional layers.

Recurrent models.

Better negative example sampling

>>>>

In the following section, we discuss embedding and attention-based neural network models, which we use to motivate our proposed model in Section \ref{sec:model}.
In Section \ref{sec:experiment}, we evaluate the effectiveness of our proposed model on the task of matching musical transcriptions to audio recordings of their corresponding songs in a large database.
Finally, we discuss results and possibilities for improvement in Section \ref{sec:results}.

@@

\section{Pruning Experiment}
\label{sec:experiment}

@@

\section{Results}
\label{sec:results}

@@

While our proposed approach has proven effective, there is room for improvement.
The model may be able to further differentiate between similar and dissimilar sequences if the dimensionality of the embedded space was increased, at the cost of a linear increase in runtime.
Alternatively, choosing negative example pairs more carefully (e.g.\ using the ``harmonic embedding'' approach of \cite{schroff2015facenet}) may further improve discrimination.
Finally, evaluating this approach on more traditional sequence retrieval tasks which allow more stringent assumptions to be made about the correct match would facilitate comparison to existing pruning techniques.
For researchers interested in utilizing and reproducing our results, code is available online.\footnote{\href{http://github.com/craffel/sequence-embedding}{\texttt{http://github.com/craffel/sequence-embedding}}}
